

\section{Periods}
Doodson [19NNN] as a guide.

Given the many possible base periods in the solar system (day, month, year, years of the other 7 planets, weighted sums and differences of those periods), the mere fact that a combination can be found that results in something 'close' [scafetta! grr. NNNN] to a period of interest is not actually very meaningful. This serves as a warning to us (all) that the adage "seek and ye shall find" warrants the corollary [NNNN] "But be careful if you have to search too hard".

A simple implementation of this corollary is to require that the multipliers be small integers. 'small' is, of course, also a vague term. But, in looking at resonances, Jupiter and Saturn have one at 5:2 (5 Jupiter years vs. 2 Saturn years, having a period of NNN years), and Earth and Venus have an excellent match at 8:13 (NNN years residual). Since the number of possible resonances/periods also increases as 9 C N, where N is the number of bodies being considered (9 = the moon plus 8 planets), one also should favor using the fewest possible interacting bodies. 9C2 = 36. 9C3 = (9*8*7)/(6) = 84.

It's also the case that if you give a mathematician enough numbers, they can add and subtract multiples of them to get any result you want, and can find (invent)  a pattern between them. For instance, the earth and Venus have near resonances at 3:5, 5:8, 8:13 -- successive terms in the Fibonacci series. The quality of match degrades further on. But it's a reminder that simply looking for numerically interesting relationships and correspondences is a) not sufficient and b) guaranteed to succeed, if one looks hard enough.

Periods to work with:\\
Earth Sidereal Day\\
Lunar Sidereal Month\\
Earth Tropical Year\\
Earth Anomalistic Year\\
Mercury, Venus, Mars, Jupiter, Saturn, Uranus, Neptune years\\
Lunar node\\
Lunar Precession\\

